# R-Markdown Examples



<!-- Place your kit's code here -->
  <script src="https://kit.fontawesome.com/bb450ff670.js" crossorigin="anonymous"></script>

<i class="fas fa-check"></i>
<i class="fas fa-info-circle"></i>
<i class="fas fa-fire"></i>
<i class="fas fa-exclamation-circle"></i>
<i class="fas fa-exclamation-triangle"></i>
<i class="fas fa-cogs"></i>
<i class="far fa-thumbs-up"></i>
<i class="far fa-thumbs-down"></i>
<i class="far fa-file-certificate"></i>
<i class="far fa-lightbulb"></i>
\
<i class="fab fa-twitter"></i>
<i class="fab fa-github"></i>
<i class="fab fa-bitbucket"></i>

***

<span style="font-size: 3rem;">
  <span style="color: Mediumslateblue;">
  <i class="fas fa-camera"></i>
  </span>
</span>

<p>Styled Font Awesome icons (size and color):</p>
<i class="fas fa-cloud" style="font-size:24px;"></i>
<i class="fas fa-cloud" style="font-size:36px;"></i>
<i class="fas fa-cloud" style="font-size:48px;color:red;"></i>
<i class="fas fa-cloud" style="font-size:60px;color:lightblue;"></i>

::: {.theorem #pyth name="Pythagorean theorem"}
For a right triangle, if $c$ denotes the length of the hypotenuse
and $a$ and $b$ denote the lengths of the other two sides, we have

$$a^2 + b^2 = c^2$$
:::

\@ref(thm:pyth)

- article
- color
- site

::: {.definition #def01 name="Accounting sales"}
this is accounting sales
:::

accounting sales, see (\@ref(definition:def01))

::: {.definition #def02 name="Commercial sales"}
this is commercial sales
:::

commercial sales, see (\@ref(def:def02))

::: {.example #exm01 name="Example of Accounting sales"}
this is accounting sales, example
:::

Example accounting sales, see (\@ref(exm:exm01))


```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.table.format = function() {
  if (knitr::is_latex_output()) 'latex' else 'pandoc'
})
```

## raw html

```{=html}
<p>Any <strong>raw</strong> HTML content works here.
For example, here is a Youtube video:</p>

<iframe width="100%" height="400"
  src="https://www.youtube.com/embed/s3JldKoA0zw?rel=0"
  frameborder="0" allow="autoplay; encrypted-media"
  allowfullscreen></iframe>
```

## verbatim
::: {.verbatim data-latex=""}
We show some _verbatim_ text here.
:::

## custom blocks

::: {.infobox .note data-latex="{note}"}
**NOTICE!**

Thank you for noticing this **new notice**! Your noticing it has
been noted, and _will be reported to the authorities_!
:::

:::: {.infobox .tip data-latex="tip"}

Include the actual content here.

::::

:::: {.infobox .warning data-latex="warning"}

Include the actual content here.

::::

:::: {.infobox .caution data-latex="caution"}

Include the actual content here.

::::

\newpage 

## Awesome

::: {.noteblock data-latex=""}
NOTE!!! tada! Thank you for noticing this **new notice**! Your noticing it has been noted, and _will be reported to the authorities_!
multiple lines.
:::

::: {.tipblock data-latex=""}
TIP!!! Thank you for noticing this **new notice**! Your noticing it has been noted, and _will be reported to the authorities_!
multiple lines.
:::

::: {.warningblock data-latex=""}
WARNING!!! Thank you for noticing this **new notice**! Your noticing it has been noted, and _will be reported to the authorities_!
multiple lines.
:::

::: {.cautionblock data-latex=""}
CAUTION!!! Thank you for noticing this **new notice**! Your noticing it has been noted, and _will be reported to the authorities_!
multiple lines.
:::

::: {.importantblock data-latex=""}
IMPORTANT!!! Thank you for noticing this **new notice**! Your noticing it has been noted, and _will be reported to the authorities_!
multiple lines.
:::

***

We define an R function `box_args()` to generate the arguments
for the box:

```{r}
box_args <- function(
  vrulecolor = 'white',
  hrule = c('\\abLongLine', '\\abShortLine', ''),
  title = '', vrulewidth = '0pt',
  icon = 'Bomb', iconcolor = 'black'
) {
  hrule <- match.arg(hrule)
  sprintf(
    '[%s][%s][\\textbf{%s}]{%s}{\\fa%s}{%s}',
    vrulecolor, hrule, title, vrulewidth, icon, iconcolor
  )
}
```

Pass some arguments to the `awesomeblock` environment through
an inline R expression:

::: {.awesomeblock data-latex="`r box_args(title = 'NOTICE!')`"}
Thank you for noticing this **new notice**!

Your noticing it has been noted, and _will be reported to
the authorities_!
:::

## mytables {#mynewtab}

[test](#new_tab)  
\@ref(mynewtab)  
\@ref(tab:tab01)  
(Section \@ref(equations))  

### DT

```{r }
library(data.table)
library(DT)

test <- fread(
   "query; key
   rep01; article site color
   rep02; article color
   rep03; color site", sep=";"
)

datatable(test, caption = "Table Test", filter = 'top' )

datatable(
  iris,
  options = list(dom = 'Pfrtip', columnDefs = list(list(
    searchPanes = list(show = FALSE), targets = c(2,4)
  ))),
  extensions = c('Select', 'SearchPanes'),
  selection = 'none'
)

```



The LaTeX environment `tiny` is only generated for LaTeX output.

```{r, include=knitr::is_latex_output()}
knitr::asis_output('\n\n\\begin{tiny}')
```

```{r}
knitr::kable(mtcars)
```

```{r, include=knitr::is_latex_output()}
knitr::asis_output('\\end{tiny}\n\n')
```

By comparison, below is the table with the normal font size.

```{r}
knitr::kable(
  head(mtcars[, 1:8], 10), booktabs = TRUE, label = "tab01",
  caption = 'Caption here of this table 01'
)
```

Tables, see (\@ref(tab:tab01))

url <- "https://bookdown.org/yihui/rmarkdown-cookbook/images/"
pic <- "warning.png"
download.file(paste0(url, pic), file.path("images", pic), mode = "wb")

download.file(
"https://bookdown.org/yihui/rmarkdown-cookbook/libs/gitbook/css/style.css", "images/style2.css")